Risk Perceptions for Wearable Devices

### 2015-03-06 tex-inputs/related_work.tex
finished smartphone related work

\subsection{Ubiquity and Wearable Devices}
Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}. Many researchers have worked to study how privacy can be preserved in the presence ubiquitous devices. Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy}, protocols for anonymous communication {cornelius2008anonysense}, evaluation metrics for privacy ~\cite{scholtz2004toward}, and privacy models ~\cite{hong2004privacy, jiang2002approximate}. However, none of these works attempted to quantify or rank user concern over different privacy risks.

@@

\subsection{Smartphones}
Many researchers have attempted to study user concerns about security or privacy issues associated with their smartphones. Research shows that perceptions of risk change as computing systems change. Chin et. al\ investigate how user attitudes toward security and privacy for smarphones differ from attitudes for traditional computing systems, and find that these attitudes differ significantly ~\cite{chin2012measuring}. How people use these devices had also changed. Palen et. al\ track smartphone users for six weeks to find rapid modifications in behaviors with respect to context and the social appropriateness of phone use cite\{palen2000going}. People also perceive and behave without a realistic understanding of the risks they are taking. Felt et. al\ examine the Android permission system and find that 17\% of participants paid attention to permissions, and only 3\% comprehended what these permissions meant.

%%% There's way more work in this area that needs to be cited (look at stuff by Janne Lindqvist, Norman Sadeh, Patrick Kelley, and Jason Hong). At the very least, if you don't add new citations, you absolutely need to say 2-3 sentences about the three papers that you did cite. Though I strongly urge you to add more.

>>>>

\subsection{Ubiquitous and Wearable Devices}
Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}. Many researchers have worked to study how privacy can be preserved in the presence ubiquitous devices. Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy}, protocols for anonymous communication {cornelius2008anonysense}, evaluation metrics for privacy ~\cite{scholtz2004toward}, and privacy models ~\cite{hong2004privacy, jiang2002approximate}. However, none of these works attempted to quantify or rank user concern over different privacy risks.

@@

\subsection{Smartphones}
Many researchers have attempted to study user concerns about security or privacy issues associated with their smartphones. Research shows that perceptions of risk change as computing systems change. Chin et. al\ investigate how user attitudes toward security and privacy for smarphones differ from attitudes for traditional computing systems, finding that these attitudes differ significantly ~\cite{chin2012measuring}. How people use these smartphones was also unlike other computing systems. Palen et. al\ track smartphone users for six weeks to find rapid modifications in behaviors with respect to context and the social appropriateness of phone use cite\{palen2000going}. People also perceive and behave without a realistic understanding of the risks they are taking. Felt et. al\ examine the Android permission system and find that 17\% of participants paid attention to permissions, and only 3\% comprehended what these permissions meant.

Smartphones enabled new systems which used new types of data which were previously hard to measure. Users tend to use these applications for their benefit, but do not think of the privacy implications. Lindqvist et. al\  studies a popular location tracking application, and find that people share their location information for gaming, signaling availability to friends, and more withou concern for privacy implications of broadcasting this information \cite{lindqvist2011m}. Tsai et. al\ found that mobile users do get feedback about releasing data, such as who has viewed that you were at a certain location, greatly impacts user behaviors \cite{Tsai2009}. However, this type of feedback is not generally provided to users. There are still many unresolved concerns, such as the opaqueness which prevents knowledge of what applications are doing with given data, along with rogue applications which steal your data \cite{1_kane_2010, zhou2011taming}.
